Stress Analysis in Social Media

### 2023-06-03 paper/paper.tex
Fix conflicts

The dataset that is used in this paper was introduced in a paper which collected posts from a social media webside called Reddit~\citep{dreaddit}.
On that website users can create posts in communities which focus on specific topics called subreddits.

>>>>

The dataset that is used in this paper was introduced in a paper which collected posts from a social media webside called Reddit~\citep{turcan-mckeown-2019-dreaddit}.
On that website users can create posts in communities which focus on specific topics called subreddits.
